Incentivizing Exploration with Unbiased History

### 2018-11-01 3level.tex
information graph -> info-graph
update figure
Started revising the 3-level policy.

\section{Adaptive Policy with Three Levels}
\label{sec:3level}
\swcomment{rewrote below}
Now we demonstrate how to design a 3-level policy to incentivize
adaptive exploration and improve the $O(T^{2/3})$ regret rate to
$\tilde O(T^{4/7})$. In \Cref{sec:llevel}, we will show how to extend
this idea to achieve a regret rate of $\tilde O(T^{1/2})$. For
simplicity, we will focus on the setting with 2 arms\niedit{, although our results can be extended to a constant number of arms $K$}. \nicomment{I think that's true, but if not, then we're not focusing on 2 arms for ``simplicity''.} \jmcomment{It is true. We only show this extension for $l$-level tho.}

The policy consists of three phases, each of which corresponds to a
level (see Figure~\ref{fig:3level}).  In the first level, the policy
performs the first round of exploration over the first
$(S\cdot T_1\cdot \GdT)$ agents, where $T_1 = T^{4/7}\log^{-1/7}(T)$
and $S = 2^{10}\log(T)$. In particular, the policy partitions
the agents into $S$ groups such that each group consists of $T_1$ runs
of \ALGG with $\GdT$ rounds. In the second level, the policy performs
further exploration on the next $(S\cdot T_2)$ agents by incorporating
data collected in the first level, where
$T_2 = T^{6/7}\log^{-5/7}(T)$. The agents are again partitioned into
$S$ groups such that the agents in the $s$-th group are shown the same
sub-history from the $s$-th group in the first level. In the third
level, the policy exploits by showing all remaining agents the entire
history from the first two levels. \nicomment{This comment applies to the 2level too; why not allow the guys within the last level see each other?  Seems like this would still work but be more of a headache to prove -- would have to argue the empirical means can't move around too much in the sub-terminal levels, but it makes a big qualitative difference because now everyone sees a vanishingly small fraction of the history whereas with this modification a fraction approaching 1 of the people see a fraction approaching 1 of the history.} \jmcomment{To do it for the last level is actually easy. It would be headache to do it for the second level as we want to prove anti-concentration in the second level. On the other hand, we have the property that agents see $1/polylog$ fraction of history in our final result for $l$-level. A different point of view is that, seeing each other requires more interaction, our policy has the nice property that the interaction is very minimal except the initial greedy runs.}

@@

\begin{theorem}
\label{thm:3level}
The 3-level recommendation policy gets expected regret $O(T^{4/7} \log^{6/7}(T))$. 
\end{theorem}

@@

\begin{figure}[H]
\centering
\begin{tikzpicture}  
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw (\x+1,1)--(\x+1,2);
 \draw(\x+0.2,1)--(\x+1,2);
 \draw(\x+0.6,1)--(\x+1,2);
 \draw(\x+1.4,1)--(\x+1,2);
 \draw(\x+1.8,1)--(\x+1,2);
 \draw(\x+0.4,0)--(\x+0.4,1); 
 \draw(\x+0.8,0)--(\x+0.8,1); 
 \draw (\x+1.2,0)--(\x+1.2,1); 
 \draw(\x+1.6,0)--(\x+1.6,1);  
 \node at(\x+1,2.5){$T_2$};
 \node at(\x+0.2, 0.5){$\GdT$};
 \node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdot$};
 \node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.8, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$}; 
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ runs};
 }
  \node at(5,4.5){$T -S(T_1 \cdot \GdT + T_2)$};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Levle 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$S$ groups};

\end{tikzpicture}
\caption{Structure of the information graph for the 3-level
  Policy. Each red box in level 1 corresponds to $T_1$ \ALGG paths of
  length $\GdT$. The sub-history of each red box is then aggregated and
  sent to a corresponding purple box of agents in level 2. Then the
  entire history of levels 1 and 2 is aggregated and shown to all
  agents in level 3.}
\label{fig:3level}
\end{figure}
% \swcomment{check the figure caption above. can we index the indicate
%   there are $S$ groups in the figure?}

>>>>

\section{Adaptive exploration with a three-level disclosure policy}
\label{sec:3level}

The two-level policy from the previous section implements the explore-then-exploit paradigm using a basic design with parallel full-disclosure paths. The next challenge is to implement \emph{adaptive exploration}, and go below the $T^{2/3}$ barrier. We accomplish this using a construction that adds a middle level to the info-graph. This construction also provides intuition for the main result, the multi-level construction presented in the next section. For simplicity, we assume $K=2$ arms.

\begin{figure}[t]
\centering
\begin{tikzpicture}
 \filldraw[fill=green!20!white]
 (0,4)--(10,4)--(10,5)--(0,5)--cycle;
 \foreach \x in {0,3,8}
 {
 \filldraw[fill=blue!20!white]
 (\x+0,2)--(\x+2,2)--(\x+2,3)--(\x+0,3)--cycle;
 \draw (\x+1,3)--(5,4);
 \filldraw[fill=red!20!white]
 (\x+0,0)--(\x+2,0)--(\x+2,1)--(\x+0,1)--cycle;
 \draw (\x+1,1)--(\x+1,2);
 \draw(\x+0.33,1)--(\x+1,2);
 \draw(\x+1.66,1)--(\x+1,2);
 %\draw(\x+1.4,1)--(\x+1,2);
 %\draw(\x+1.8,1)--(\x+1,2);
 \draw(\x+0.66,0)--(\x+0.66,1);
 \draw(\x+1.33,0)--(\x+1.33,1);
% \draw (\x+1.2,0)--(\x+1.2,1);
 %\draw(\x+1.6,0)--(\x+1.6,1);
 \node at(\x+1,2.5){$N_2$ rounds};
 \node at(\x+0.33, 0.5){$\GdT$};
 %\node at(\x+0.6, 0.5){$\cdot$};
 \node at(\x+1.0, 0.5){$\cdots$};
 %\node at(\x+1.4, 0.5){$\cdot$};
 \node at(\x+1.66, 0.5){$\GdT$};
 %\node at(\x+1,0.5){$T_1 \cdot \GdT$};
 \draw [decorate,decoration={brace,amplitude=10pt},xshift=0pt,yshift=0pt] (\x+2,-0.2) -- (\x+0,-0.2) node [black,midway,yshift=-0.6cm] {$T_1$ paths};
 }
  \node at(5,4.5){all remaining rounds};
  \node at (6,0.5){$\cdots$};
  \node at (7,0.5){$\cdots$};
  \node at (6,2.5){$\cdots$};
  \node at (7,2.5){$\cdots$};
  \node at(-1,0.5){\textbf{Level 1}};
  \node at(-1,2.5){\textbf{Level 2}};
  \node at(-1,4.5){\textbf{Level 3}};
  \draw[->] (11,0)--(11,5);
  \node at(11.5,2.5)[ rotate=90]{Time};

  \draw [decorate,decoration={brace,amplitude=10pt,aspect=0.33},xshift=0pt,yshift=0pt] (10,1.8) -- (0,1.8) node [black,pos=0.33,xshift = 0cm,yshift=-0.6cm] {$T_2$ groups};

\end{tikzpicture}
\caption{Info-graph for the three-level policy. Each red box in level 1 corresponds to $T_1$ full-disclosure paths of length $\GdT$ each.}
\label{fig:3level}
\end{figure}

The new policy, called the \emph{three-level policy}, is as follows
 (see Figure~\ref{fig:3level}).

\begin{construction}
The info-graph consists of three levels: the first two correspond to \emph{exploration}, and the third implements \emph{exploitation}. Like in the two-level policy, the first level consists of multiple full-disclosure paths of length $\fdpL$ each, and each agent $t$ in the exploitation level sees full history from exploration. The middle layer is what ensures adaptive exploration. It consists of $T_2$ disjoint subsets of $N_2$ agents each, called \emph{second-level groups}. Each second-level group $S$ has the following property:
\begin{align}\label{eq:group-defn}
\text{all nodes in $S$ are connected to the same nodes outside of $S$, but not to one another.}
\end{align}

The full-disclosure paths in the first level are also split into $T_2$ disjoint subsets, called \emph{first-level groups}. Each first-level group consists of $T_1$ full-disclosure paths, for the total of $T_1\cdot T_2\cdot \fdpL$ rounds in the first layer. There is a 1-1 correspondence between first-level groups $S_1$ and second-level groups $S_2$, whereby each agent $t\in S_2$ observes the full history from the corresponding group $S_1$. More formally, agent $t$ is connected to the last node of each full-disclosure path in $S_1$. In other words, this agent receives message
    $m_t = \SubH{V(S_1)}$,
where $V(S_1)$ is the set of all rounds in $S_1$. 
\end{construction}

\begin{theorem}
\label{thm:3level}
For two arms, the three-level policy
achieves regret
\[ \reg(T) \leq O\left( T^{4/7}\, \log T \right).\]
This is achieved with parameters
    $T_1 = T^{4/7}\log^{-1/7}(T)$,
    $T_2 = 2^{10}\log(T)$, and
    $N_2 = T^{6/7}\log^{-5/7}(T)$.
\end{theorem}

\ascomment{stopped here.}

@@

@@
